---
title: "Template for a short single author DOCX report in RMarkdown"
author: "Daniel Rodríguez"
date: "`r Sys.Date()`"
abstract: | 
    # Abstract
    This DOCX template is meant for short reports with no figure and table
    numbering, and with a single author.
    
    **Keywords:** Word 1, Word 2, Word 3.
output:
   bookdown::word_document2:
    toc: yes
    toc_depth: 5
    reference_docx: "Single-author-report_docx-ref-01.docx"
csl: elsevier-harvard.csl
bibliography: references.bib
---

```{r setup01, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r setup02}
knit_print.data.frame <- function(x, ...) {
  res <- paste(c("", "", knitr::kable(x, caption = caption)), collapse = "\n")
  knitr::asis_output(res)
}

registerS3method(
  "knit_print", "data.frame", knit_print.data.frame,
  envir = asNamespace("knitr")
)
```

# Heading 1
## Heading 2
### Heading 3
#### Heading 4
##### Heading 5
Paragraph 1 of normal text, it is extended to two lines in purpose to check the format of the space in between lines of the same paragraph.

Paragraph 2 of normal text, it is extended to two lines in purpose to check the
format of the space in between lines of the same paragraph.

Citations can be inserted in text, with ease by using the Zotero citation key(s)
(`@citation_key`) of the source(s) to cite. A citation at the end of the
sentence is easily applied with `[@citation_key]`. For example by citing my own
first paper at the end of this sentence
[@rodriguezleonVariacionAbundanciaRelativa2019]. The previous sentence looks
like this **`For example by citing my own first paper by the end of this
sentence [@rodriguezleonVariacionAbundanciaRelativa2019]`** in the RMarkdown
document. Meanwhile, a citation as the noun of the sentence can be inserted by
using `@citation_key`. Here, @rodriguezleonVariacionAbundanciaRelativa2019 is
again an example of this, which looks like this
**`rodriguezleonVariacionAbundanciaRelativa2019 is again an example of this`**
in the RMarkdown document.

# Making a table

With the *"df_print: kable"* any data frame that is printed inside the document
is printed as a table using *"knitr::kable()"*. For example by printing the head
of the data frame of the **"cars"** data set, which is printed here with the *```r ` ``* inline code command:

```{r}
caption <- "Head of cars dataset data frame"
cars %>% head
```

For the bibliography, it is only required to have a last section in the document
with the "Bibliography"or "References" title. The bibliography will by
automatically inserted from the specified BibTex (.bib) file in the YAML section
of the RMarkdown document (e.g. `` bibliography: references.bib ``), which
should be stored in the same directory folder as the corresponding RMarkdown
document file.

# References
