---
title: "Template for a DOCX report in RMarkdown"
author:
  - Author One, author info.^[author info., e-mail@example.org]
  - Author Two, author info.^[author info., e-mail@example.org]
date: "`r Sys.Date()`"
abstract: | 
    # Abstract
    This DOCX template is meant for short reports with no figure and table 
    numbering.
    
    **Keywords:** Word 1, Word 2, Word 3.
output:
   #pdf_document:
   word_document: 
     toc: yes
     toc_depth: 5
     reference_docx: Report_docx-ref.docx
csl: elsevier-harvard.csl
bibliography: references.bib
---
# Establishing the settings for the Rmd document
On a normal Rmd document the setup code tends to be in one(or several) setup
code chunk(s) that are not rendered inside the final output file, by using the
``include = FALSE`` chunk option. However, here the setup chunks are included in
the output document to show there the structure of the Rmd document more
explicitly.

The following chunk shows the typical setup chunk of an Rmd document, setting the `echo` chunk option to `TRUE`inside the Rmd document. Here I also load the packages I know will be used along the document (e.g. Tidyverse (or specific tidyverse packages), and here),.
```{r setup, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

The following chunk defines a new function for printing data frames within the
Rmd document, modifying the default options of the ``knitr::kable()`` function.
The new data frame printing function needs two objects to work. It requires the
data frame to print, which is automatically given to the function when a data
frame is printed within the Rmd document, and a caption. The latter has to be
defined by storing the caption text in a object called caption, which will be
used by the function to produce the table caption.

```{r setup02}
knit_print.data.frame <- function(x, ...) {
  res <- paste(c("", "", knitr::kable(x, caption = caption)), collapse = "\n")
  knitr::asis_output(res)
}
```

The chunk below registers the method of the previously defined
`knit_print.data.frame` function under the `knit_print` function.
```{r setup03}
registerS3method(
  "knit_print", "data.frame", knit_print.data.frame,
  envir = asNamespace("knitr")
)
```

# Heading 1
## Heading 2
### Heading 3
#### Heading 4
##### Heading 5
Paragraph 1 of normal text, it is extended to two lines in purpose to check the
format of the space in between lines of the same paragraph.


Paragraph 2 of normal text, it is extended to two lines in purpose to check the
format of the space in between lines of the same paragraph.

Citations can be inserted in text, with ease by using the Zotero citation key(s)
(`@citation_key`) of the source(s) to cite. A citation at the end of the
sentence is easily applied with `[@citation_key]`. For example by citing my own
first paper at the end of this sentence
[@rodriguezleonVariacionAbundanciaRelativa2019]. The previous sentence looks
like this **`For example by citing my own first paper by the end of this
sentence [@rodriguezleonVariacionAbundanciaRelativa2019]`** in the RMarkdown
document. Meanwhile, a citation as the noun of the sentence can be inserted by
using `@citation_key`. Here, @rodriguezleonVariacionAbundanciaRelativa2019 is
again an example of this, which looks like this
**`rodriguezleonVariacionAbundanciaRelativa2019 is again an example of this`**
in the RMarkdown document.

# Making a table

As we defined and register the function `knit_print.data.frame` on the setup chunks at the beginning of the document, any data frame that is printed inside the document is printed as a table using the `knit_print.data.frame`, which is a modifed version of the `knitr::kable()` function. For example by printing the head of the data frame of the **"cars"** data set.
```{r}
caption <- "Head of cars dataset data frame"
cars %>% head
```

For the bibliography, it is only required to have a last section in the document
with the "Bibliography"or "References" title. The bibliography will by
automatically inserted from the specified BibTex (.bib) file in the YAML section
of the RMarkdown document (e.g. `` bibliography: references.bib ``), which
should be stored in the same directory folder as the corresponding RMarkdown
document file.

# References